### 2013-06-05 Tex/chapters/model.tex
weiteren Inhalt hinzugefügt

\subsection{Model}
    The used model is a modified 2D Ising model where the sites are
    displaced nodes of a square lattice with periodic boundary
    conditions. The displacement is randomly gauss distributed with the
    standard deviation \(\sigma\). This \(\sigma\) is also called
    \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)
    where \(<i,j>\) refers to by edges connected nodes.
    The edges are constructed according to the in section
    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
    called \emph{interaction}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\).

>>>>

\subsection{Model}
    The used model is a modified 2D Ising model where the \(N\)sites are
    displaced nodes of a square lattice of edgelength \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{<i,j>}J_{ij}s_{i}s_{j}\)
    where \(<i,j>\) refers to by edges connected nodes.
    The edges are constructed according to the in section
    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
    called \emph{interaction}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\).

\subsection{Determining the Critical Temperature $T_c$}
    Because the searched for property -- the critical temperature \(T_c\)
    -- is only defined for infinite systems, hence every computer
    simulation will show some \emph{finte size effects}.
    [vielleicht Bild von intensiver Größe?]
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{Newman1998} which also yield the critical
    exponents [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma
    die exponenten reproduziert hat].\\
    Though if one is just interested in the critical Temperature an
    easier approach is to find the intersections of the binder cumulants
    \(G\) \cite{Binder1981} for different system sizes \(L=\sqrt N\).\\
